---
title: "Analysis of Clustered Data"
output: html_notebook
---

### Setup:
```{r}
library(ggplot2)
library(png)
library(pheatmap)
library(NbClust)
library(cluster)
library(plyr)
library(dplyr)
library(plotly)
library(ggpubr)
library(factoextra)
library(jtools)
library(effsize)
library(fpc)
source("ASDClusteringParams.R", local= knitr::knit_global())
source("corStars.R", local= knitr::knit_global())

setwd(params$WorkingDirectory)
if (params$UsePreclusteredData){
  load(file = params$zScoredASDDataFile)
  load(file = params$zScoredHCDataFile)
} else {
  print("Run Clustering separately (Clustering.RMD to continuey")
}
allZScored = rbind(asdZScored, hcZScored)
```

### Defining function to calculate and plot group differences by measure 
```{r}
## Function to do all the group comparisons and plotting
post_hoc_analysis <- function(data, measure, grouping = "clust", adjustP = T) {
  ## Create plots
  density_plot <- ggplot(data, aes(x= data[,measure],  color = as.factor(data[,grouping]), 
      group = data[,grouping])) + geom_density() + theme_apa() + ylab("")+xlab(measure) + theme(text=element_text(family="serif"))
  
  box_plot <- ggplot(data, aes(y= as.numeric(data[,measure]),  color = as.factor(data[,grouping]), group = data[,grouping])) + 
      geom_boxplot() +theme_apa() +ylab(measure) + theme(text=element_text(family="serif"))
  
  plot_list <- list(box_plot, density_plot)

  ## Ignrore incomplete cases
  completeCases <- list(
    Total = length(na.omit(data[,measure])),
    ASD1 = length(na.omit(data[data[grouping] == 1,measure])),
    ASD2 = length(na.omit(data[data[grouping] == 2,measure]))
  )
  
  ## Calcualte means
  means <- list(
    Total = mean(data[,measure], na.rm = T),
    ASD1 = mean(data[data[grouping] == 1,measure], na.rm = T),
    ASD2 = mean(data[data[grouping] == 2,measure], na.rm = T)
  )
  
  ## Calcualte SDs
  SDs <- list(
    Total = sd(data[,measure], na.rm = T),
    ASD1 = sd(data[data[grouping] == 1,measure], na.rm = T),
    ASD2 = sd(data[data[grouping] == 2,measure], na.rm = T)
  )
  
  ## Calcualte difference statistics
  ttest <- t.test(data[data[grouping] == 1, measure],data[data[grouping] == 2, measure])
  Ftest <- var.test(data[data[grouping] == 1, measure],data[data[grouping] == 2, measure])
  CohensD <- cohen.d(data[data[grouping] == 1, measure],data[data[grouping] == 2, measure], na.rm =T)
  
  ttestData <- list(
    t = as.numeric(ttest$statistic),
    p = ttest$p.value,
    p.adj = ttest$p.value * adj.Scalecount,
    df = ttest$parameter
  )
  if (!adjustP) {
    ttestData$p.adj = ttestData$p
  }
  ttestData[["sig"]] <- ""
  if (ttestData$p.adj < 0.05) {ttestData[["sig"]] <- "*"}
  if (ttestData$p.adj < 0.01) {ttestData[["sig"]] <- "**"}
  if (ttestData$p.adj < 0.001) {ttestData[["sig"]] <- "***"}

    results <- list(Measure = measure, 
                        Count.Total = completeCases$Total, Mean.Total = means$Total, SD.Total = SDs$Total, 
                        Count.ASD1 = completeCases$ASD1, Mean.ASD1 = means$ASD1, SD.ASD1 = SDs$ASD1,
                        Count.ASD2 = completeCases$ASD2, Mean.ASD2 = means$ASD2, SD.ASD2 = SDs$ASD2, 
                        F.Value = Ftest$statistic,F.df1 =Ftest$parameter[1],F.df2 =Ftest$parameter[2], Fsig = Ftest$p.value,
                        CohensD = CohensD$estimate, t.Value = ttestData$t, t.df = ttestData$df,
                          t.p = ttestData$p, tp.adj = ttestData$p.adj, Significance = ttestData$sig
                        )
  return(list(statistics = results, plots = plot_list))
}

```


### Calculate and set the effective number of variables to correct for
```{r}
asdScales <- c("ASSQ_Total", "SRS_Total", "SRS_AWR", "SRS_COG", "SRS_COM", "SRS_MOT", "SRS_RRB")
ageVar <- "Age"
phts <- params$PosthocTestScales
multipleComparisonScales <- unlist(append(asdScales, append(phts, ageVar)))
adj.Scalecount <- getMeff(allZScored[, multipleComparisonScales])
```

## Measure Correlations
### Import the corStars File to generate lower-half correlation tables with significance stars
```{r}
## Correlation Table for ASD subjects
asdCorr <- corstars(asdZScored[,multipleComparisonScales], result="html", correction = adj.Scalecount)
fileConn<-file("../misc/corrMeasuresASD.html", "wb")
write(asdCorr,fileConn)
close(fileConn)

## Correlation Table for controls
hcCorr <- corstars(hcZScored[,multipleComparisonScales], result="html", correction = adj.Scalecount)
fileConn<-file("../misc/corrMeasuresHC.html", "wb")
write(asdCorr,fileConn)
close(fileConn)

## Correlation Table overall
allCorr <- corstars(allZScored[,multipleComparisonScales], result="html", correction = adj.Scalecount)
fileConn<-file("../misc/corrMeasuresAll.html", "wb")
write(asdCorr,fileConn)
close(fileConn)
```


## Group differences
Calculate subtype differences for ASSQ and SRS + subscales
```{r}
ASDMeasures <- data.frame()
allMeasures <- c()
plot_list <- list()
for (asdS in asdScales) {
  analysis <- post_hoc_analysis(asdZScored,asdS)
  ASDMeasures <- rbind(ASDMeasures, analysis$statistics)
  plot_list <- append(plot_list, analysis$plots)
}


allMeasures <- append(allMeasures, asdScales)

ASDMeasures
write.csv(ASDMeasures, file="../misc/ASDMeasures.csv", sep=";")
if (nrow(ASDMeasures[ASDMeasures$p < 0.001,]) > 0) {ASDMeasures[ASDMeasures$p < 0.001,]$p <- "<0.001" }
write.table(ASDMeasures, "clipboard",sep="\t",col.names=NA)
ggarrange(plotlist = plot_list, ncol = 2, nrow = 2, common.legend = T, legend = "bottom")
```

### Calculate subtype differences for all other behavioral scales
```{r}
behavioralMeasures <- data.frame()
plot_list <- list()
for (pht in params$PosthocTestScales) {
  analysis <- post_hoc_analysis(asdZScored,pht)
  behavioralMeasures <- rbind(behavioralMeasures, analysis$statistics)
  plot_list <- append(plot_list, analysis$plots)
}

allMeasures <- append(allMeasures, params$PosthocTestScales)
behavioralMeasures
write.csv(behavioralMeasures, file="../misc/behavioralMeasures.csv", sep=";")
if (nrow(behavioralMeasures[behavioralMeasures$p < 0.001,]) > 0) {behavioralMeasures[behavioralMeasures$p < 0.001,]$p <- "<0.001" }
write.table(behavioralMeasures, "clipboard",sep="\t",col.names=NA)
ggarrange(plotlist = plot_list, ncol = 2, nrow = 2, common.legend = T, legend = "bottom")
```


### Calculate subtype differences for age
```{r}
ageData <- data.frame()
plot_list <- list()
  analysis <- post_hoc_analysis(asdZScored,"Age")
  ageData <- rbind(ageData, analysis$statistics)
  plot_list <- append(plot_list, analysis$plots)

allMeasures <- append(allMeasures, c("Age"))
ageData
write.csv(ageData, file="../misc/ageData.csv", sep=";")
if (nrow(ageData[ageData$p < 0.001,]) > 0) {ageData[ageData$p < 0.001,]$p <- "<0.001" }
write.table(ageData, "clipboard",sep="\t",col.names=NA)
ggarrange(plotlist = plot_list, ncol = 2, nrow = 2, common.legend = T, legend = "bottom")
```

### Calculate subtype differences for MRI Quality measures
```{r}
qualityMeasures <- data.frame()
qm <- c("SNR", "FWHM", "EFC", "FBER", "Qi1", "CNR")
plot_list <- list()
adj.Scalecount <- getMeff(allZScored[, append(multipleComparisonScales, qm)])
for (qc in qm) {
  analysis <- post_hoc_analysis(asdZScored,qc, adjustP = T)
  qualityMeasures <- rbind(qualityMeasures, analysis$statistics)
  plot_list <- append(plot_list, analysis$plots)
}

adj.Scalecount <- getMeff(allZScored[, multipleComparisonScales])

qualityMeasures
write.csv(qualityMeasures, file="../misc/qualityMeasures.csv", sep=";")
qualityMeasures[qualityMeasures$p < 0.001,]$p <- "<0.001" 
write.table(qualityMeasures, "clipboard",sep="\t",col.names=NA)
ggarrange(plotlist = plot_list, ncol = 2, nrow = 2, common.legend = T, legend = "bottom")

## Also generate paired scatter plots with group information
## first by diagnosis
my_cols <- c("#67BAE6", "#7EE696")  
pairs(allZScored[,qm], pch = 19,  cex = 0.5,
      col = my_cols[allZScored$Subject+1],
      upper.panel = NULL)

## first then within ASD for cluster
my_cols <- c("#f8766d", "#00bfc4")  
pairs(asdZScored[,qm], pch = 19,  cex = 0.5,
      col = my_cols[asdZScored$clust],
      upper.panel = NULL)
```

### Also calculate all group differences by diagnosis
```{r}
hcvASD <- data.frame()
plot_list <- list()
allZScored = rbind(asdZScored, hcZScored)
allZScored$SubjectIncr <- allZScored$Subject+1
for (msr in allMeasures) {
  analysis <- post_hoc_analysis(allZScored,msr, grouping = "SubjectIncr")
  hcvASD <- rbind(hcvASD, analysis$statistics)
  plot_list <- append(plot_list, analysis$plots)
}

hcvASD
write.csv(hcvASD, file="../misc/hcvASD.csv", sep=";")
if (nrow(hcvASD[hcvASD$p < 0.001,]) > 0) {hcvASD[hcvASD$p < 0.001,]$p <- "<0.001" }
write.table(hcvASD, "clipboard",sep="\t",col.names=NA)
ggarrange(plotlist = plot_list, ncol = 2, nrow = 2, common.legend = T, legend = "bottom")
```


### Generate additional line plots comparing SRS-Subscales between ASD and HC 
```{r}
SRS_Subscales <- c("SRS_AWR", "SRS_COG", "SRS_COM", "SRS_DSMRRB", "SRS_MOT", "SRS_SCI", "SRS_RRB")

srsData <- data.frame(
  Mean =  
    apply(asdZScored[SRS_Subscales],MARGIN= 2, FUN= mean, na.rm = T),
  SD = 
    apply(asdZScored[SRS_Subscales],MARGIN= 2, FUN= sd, na.rm = T), 
  Scale = 
    SRS_Subscales)

srsData$Subject <- 1
srsHcData <- data.frame(
  Mean =  
    apply(hcZScored[SRS_Subscales],MARGIN= 2, FUN= mean, na.rm = T),
  SD = 
    apply(hcZScored[SRS_Subscales],MARGIN= 2, FUN= sd, na.rm = T), 
  Scale = 
    SRS_Subscales)
srsHcData$Subject <- 0
srsData <- rbind(srsData,srsHcData)

ggplot(srsData[order(srsData$Scale),], aes(x=Scale, y=Mean, fill=as.factor(Subject), color = as.factor(Subject))) + geom_path(aes(x=Scale, y=Mean, group=as.factor(Subject), color = as.factor(Subject))) +
  geom_point(position=position_dodge(0.1))+ 
   geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD, color = as.factor(Subject)), width=.1,
                position=position_dodge(0.1))+theme_apa() + ylim(c(0,75)) + theme(axis.text.x = element_text(angle=90), text=element_text(family="serif")) +# + guides()
  scale_color_manual(values=c("0" = "#67BAE6", "1" = "#7EE696"))
```

### ...as well as between ASD1 and ASD2
```{r}
srsData <- data.frame(
  Mean =  
    apply(asdZScored[asdZScored$clust == 1,SRS_Subscales],MARGIN= 2, FUN= mean, na.rm = T),
  SD = 
    apply(asdZScored[asdZScored$clust == 1,SRS_Subscales],MARGIN= 2, FUN= sd, na.rm = T), 
  Scale = 
    SRS_Subscales)

srsData$Cluster = 1
srsClust2Data <- data.frame(
  Mean =  
    apply(asdZScored[asdZScored$clust == 2,SRS_Subscales],MARGIN= 2, FUN= mean, na.rm = T),
  SD = 
    apply(asdZScored[asdZScored$clust == 2,SRS_Subscales],MARGIN= 2, FUN= sd, na.rm = T), 
  Scale = 
    SRS_Subscales)

srsClust2Data$Cluster <- 2
srsData <- rbind(srsData,srsClust2Data)

ggplot(srsData[order(srsData$Scale),], aes(x=Scale, y=Mean, fill=as.factor(Cluster), color = as.factor(Cluster))) + geom_path(aes(x=Scale, y=Mean, group=as.factor(Cluster), color = as.factor(Cluster))) +
  geom_point(position=position_dodge(0.1))+
   geom_errorbar(aes(ymin=Mean-SD, ymax=Mean+SD, color = as.factor(Cluster)), width=.1,
                position=position_dodge(0.1))+  ylim(c(0,75))  +theme_apa()+ theme(axis.text.x = element_text(angle=90), text=element_text(family="serif"))
```

### Generate Table with comorbidities
```{r}
dx_fields <- c("DX_01", "DX_02", "DX_03", "DX_04", "DX_05", "DX_06", "DX_07", "DX_08", "DX_09", "DX_10")
comorbidities_ASD1 <- table(unlist(apply(asdZScored[asdZScored$clust == 1,dx_fields], 1, unique)))
comorbidities_ASD2 <- table(unlist(apply(asdZScored[asdZScored$clust == 2,dx_fields], 1, unique)))

comData <- data.frame(comorbidities_ASD1)
comData$percentageASD1 <- comData$Freq/ nrow(asdZScored[asdZScored$clust == 1,])
names(comData)[names(comData) == "Freq"] <- "ASD1"

comData_t <- data.frame(comorbidities_ASD2)
comData_t$percentageASD2 <- comData_t$Freq/ nrow(asdZScored[asdZScored$clust == 2,])
names(comData_t)[names(comData_t) == "Freq"] <- "ASD2"

comData <- join(comData, comData_t, by= "Var1")
nrow(asdZScored[asdZScored$clust==1,])
comData <- comData[order(comData$ASD1,decreasing = T),]
write.table(comData, "clipboard",sep="\t",col.names=NA)
write.csv(comData, file = "../misc/asdComorbs.csv")
```

## Cluser Quality
### Principal component analysis to show connection between clustering and main factors
```{r}
asdZScored.pca <- prcomp(asdZScored[,features])
asdZScored.pca$sdev
length(asdZScored.pca$sdev[asdZScored.pca$sdev > 1])
plot(asdZScored.pca, type="l")
fviz_pca_ind(asdZScored.pca, fill.ind = factor(asdZScored$clust), pointshape = 21, pointsize = 2, addEllipses = T, label = "var", axes = c(1,2))+theme_apa()+ theme( text=element_text(family="serif"))
fviz_pca_ind(asdZScored.pca, fill.ind = factor(asdZScored$clust), pointshape = 21, pointsize = 2, addEllipses = T, label = "var", axes = c(2,3))+theme_apa()+ theme( text=element_text(family="serif"))
fviz_pca_ind(asdZScored.pca, fill.ind = factor(asdZScored$clust), pointshape = 21, pointsize = 2, addEllipses = T, label = "var", axes = c(1,3))+theme_apa()+ theme( text=element_text(family="serif"))
fviz_pca_ind(asdZScored.pca, fill.ind = factor(asdZScored$clust), pointshape = 21, pointsize = 2, addEllipses = T, label = "var", axes = c(1,4))+theme_apa()+ theme( text=element_text(family="serif"))
```

### Differences in counts by site and cluster
```{r}
clustXSite <- chisq.test(asdZScored$clust, asdZScored$site)
clustXProtocol <- chisq.test(asdZScored$clust, asdZScored$Protocol)
siteXProtocol <- chisq.test(asdZScored$site, asdZScored$Protocol)
clustXSite$observed
clustXSite

clustXProtocol$observed
clustXProtocol

siteXProtocol$observed
siteXProtocol
ggplot(asdZScored, aes(x=clust, y=site))+
  geom_count()
ggplot(asdZScored, aes(x=clust, y=Protocol))+
  geom_count()
ggplot(asdZScored, aes(x=site, y=Protocol))+
  geom_count()

ggplot(asdZScored, aes(y= Age, group = clust, fill=clust)) + geom_boxplot()
cor.test(asdZScored$clust, asdZScored$Age)
pairwise.t.test(asdZScored$Age, asdZScored$clust, p.adjust.method = "bonferroni")
```

### Calculate Jaccard means for different sample combinations
```{r}
bootstrapJaccardMeans <- function(sampleDescriptor, featureMatrix, boots){
  distanceMatrix <- dist(featureMatrix, method = params$Distance)
  clusterRes = hclust(distanceMatrix, params$ClusterMethod)
  groups = cutree(clusterRes, k = params$k())
  clustSize <- c(sum(groups == 1), sum(groups==2))
  clustBoot <- clusterboot(distanceMatrix, clustermethod=hclustCBI, method=params$ClusterMethod, k=params$k(), B=boots, multipleboot = T)
  clusterBootJaccardMeans <- data.frame(sample = sampleDescriptor,
                                        c1_Count = clustSize[1], c1_JaccardMean = clustBoot$bootmean[1],
                                        c2_Count = clustSize[2], c2_JaccardMean = clustBoot$bootmean[2])
  return(list(bootResult = clustBoot, jaccardMeans = clusterBootJaccardMeans))
}

## Cluster stability for subtypes
JaccardData <- bootstrapJaccardMeans("ASD", asdZScored[,features], boots = params$BootCount)$jaccardMeans
## Cluster stability for controls
JaccardData <- rbind(JaccardData, bootstrapJaccardMeans("HC", hcZScored[,features], boots = params$BootCount)$jaccardMeans)
## Cluster stability for controls + ASD
JaccardData <- rbind(JaccardData, bootstrapJaccardMeans("HC_ASD", rbind(hcZScored[,features], 
                                                                        asdZScored[,features]), boots=params$BootCount)$jaccardMeans)
## Cluster stability for controls + ASD1
JaccardData <- rbind(JaccardData, bootstrapJaccardMeans("HC_ASD1", rbind(hcZScored[,features], 
                                                                        asdZScored[asdZScored$clust==1,features]), boots=params$BootCount)$jaccardMeans)
## Cluster stability for controls + ASD2
JaccardData <- rbind(JaccardData, bootstrapJaccardMeans("HC_ASD2", rbind(hcZScored[,features], 
                                                                        asdZScored[asdZScored$clust==2,features]), boots=params$BootCount)$jaccardMeans)
kable(JaccardData)
write.table(JaccardData, "clipboard",sep="\t",col.names=NA)
```

### FreeSurfer GLM
```{r}
source("freesurfer_helper.R")

variables <- c()
hcNoMissings <- hcZScored
hcNoMissings$clust <- 3
allSubs <- rbind(asdZScored, hcNoMissings[hcNoMissings$Subject == 0,])
generateFSGDALL(allSubs, variables, params$GLMProjects$ClusteredASD$Title, directory = params$GLMFolder)


## generatingGLMAll generates a bash script for the analysis, it contains both the glm as well as glm-sim commands
## when testing or iterating through different GLM setups this can be usefull
## otherwise it might be more appropriate generate a file for all analysis manually

generateGLMALL(features= params$Features,
               title = params$GLMProjects$ClusteredASD$Title,
               contrasts = params$GLMProjects$ClusteredASD$Contrasts,
               directory = params$GLMFolder)


variables <- c("SNR")
hcNoMissings <- hcZScored
hcNoMissings$clust <- 3
allSubs <- rbind(asdZScored, hcNoMissings[hcNoMissings$Subject == 0,])
generateFSGDALL(allSubs, variables, params$GLMProjects$ClusteredASDSNR$Title, directory = params$GLMFolder)

generateGLMALL(features= params$Features,
               title = params$GLMProjects$ClusteredASDSNR$Title,
               contrasts = params$GLMProjects$ClusteredASDSNR$Contrasts,
               directory = params$GLMFolder)

variables <- c()
hcTemp <- hcZScored
hcTemp$clust <- 1
asdTemp <- asdZScored
asdTemp$clust <- 2
allSubs <- rbind(asdTemp, hcTemp[hcTemp$Subject == 0,])
generateFSGDALL(allSubs, variables, params$GLMProjects$DiagASD$Title, directory = params$GLMFolder)

generateGLMALL(features= params$Features,
               title = params$GLMProjects$DiagASD$Title,
               contrasts = params$GLMProjects$DiagASD$Contrasts,
               directory = params$GLMFolder)

## generateSimLinkCMD generates a bash script to sim-link all given subjects in one folder
## this is usefull, because subjects might be located in different source folders
## symbolic links are independent files and can be deleted without affecting the soruce
## running different iterations of this file does not change existing links 
generateSimLinkCMD(asdZScored, hcNoMissings[hcNoMissings$Subject == 0,], params$Sites, directory = params$GLMFolder)

```

### Some MRI-QM exploration
```{r}
## Heatmap of Quality measures and export of correlation table
pheatmap(cor(allZScored[,qm], use="pairwise.complete.obs"), cluster_rows = F, cluster_cols = F, display_numbers = T, fontsize = 15)

qmCorr <- corstars(asdZScored[,qm], result="html", correction = getMeff(allZScored[,qm]))
fileConn<-file("../misc/corrQMASD.html", "wb")
write(qmCorr,fileConn)
close(fileConn)

## PCA with QM to find main factors since they are correlated
pcaQMData <- na.omit(allZScored[,qm])
tmpZ <- allZScored
pcQM <- princomp(pcaQMData)
pcQM$loadings
qmComp1 <- as.matrix(pcaQMData) %*% pcQM$loadings[,1]
qmComp2 <- as.matrix(pcaQMData) %*% pcQM$loadings[,2]
allZScored$qmComp1 <- NA
allZScored$qmComp2 <- NA
allZScored[!is.na(allZScored[,"SNR"]),]$qmComp1 <- as.vector( qmComp1)
allZScored[!is.na(allZScored[,"SNR"]),]$qmComp2 <- as.vector( qmComp2)

## Testing factors for group differences
t.test(allZScored[allZScored$Subject == 1 & allZScored$clust == 1, "qmComp1"], allZScored[allZScored$Subject == 1& allZScored$clust == 2, "qmComp1"])
t.test(allZScored[allZScored$Subject == 1 & allZScored$clust == 1, "qmComp2"], allZScored[allZScored$Subject == 1& allZScored$clust == 2, "qmComp2"])

t.test(allZScored[allZScored$Subject == 1, "qmComp1"], allZScored[allZScored$Subject == 0, "qmComp1"])
t.test(allZScored[allZScored$Subject == 1, "qmComp2"], allZScored[allZScored$Subject == 0, "qmComp2"])
cor.test(allZScored$qmComp2, allZScored$SRS_Total)
```

### Post-Hoc correlation tests of hyperactivity and Signal-To-Noise Ratio
```{r}
cor.test(allZScored$SWAN_HY, allZScored$SNR)
cor.test(allZScored$C3SR_HY, allZScored$SNR)
```

### Generate overview Tables with Age ASSQ and SRS
```{r}
demVars <- c("Age", "ASSQ_Total", "SRS_Total")#, "SRS_AWR", "SRS_COG", "SRS_COM", "SRS_DSMRRB", "SRS_MOT", "SRS_SCI", "SRS_RRB")
asd <- asdZScored
asd$group <- 1
hc <- hcZScored[hcZScored$Subject == 0,]
hc$group <- 0
demData <- rbind(asd, hc)
demOverview <- data.frame

genDemCol <- function(demData, demVars, group, site, description) {
  n <-nrow(demData[demData$group  == group & grepl(site, demData$site),])
  overview <- data.frame()
  for (var in demVars) {
    vals <- demData[demData$group  == group & grepl(site, demData$site),var]
    row <- data.frame(Description = description, Group = group, Site = site, count = n, Variable = var, Mean =mean(vals, na.rm = T), SD =  sd(vals, na.rm = T))
    overview <- rbind(overview, row)
  }

  return(overview)
}

## Generate Table for all ASD and Controls
for (i in  c(0,1)) {
    demOverview <- rbind(demOverview, genDemCol(demData,demVars, i,"*", "Overall"))
}

## Generate Tables by site
for (site in unique(demData$site)) {
  for (i in  c(0,1)) {
    demOverview <- rbind(demOverview, genDemCol(demData, demVars,i,site, "By Site"))
  }
}

## Generate Tables for ASD by cluster
for (i in 1:max(asdZScored$clust)){
  demOverview <- rbind(demOverview, genDemCol(demData[demData$clust == i,], demVars, 1, "*", paste("ASD", i)))
}

write.csv(demOverview, file="demOverview.csv", sep=";")
write.table(demOverview, "clipboard",sep="\t",col.names=NA)
```